Mendelian randomization for causal inference in genome-wide association studies

### 2022-03-01 mr-review.Rmd
added text for hemani 2017

@hemani_orienting_2017

>>>>

@hemani_orienting_2017, working in the setting of two-sample MR with summary GWAS data, recognized that
measurement error in outcome and exposure can give misleading results with the inferred 
causal arrow in the wrong direction. To work around this issue, they extended 
MR with a method that infers the causal direction between two traits. Specifically, @hemani_orienting_2017 
adapt Steiger's Z test for a difference in correlations [@steiger1980tests] to assess which of the two 
traits in an analysis has the stronger correlation with the SNP instrument. That 
with the stronger correlation is treated as the exposure. @hemani_orienting_2017 
applied their test in a study of DNA methylation and gene expression, where either 
direction of causality is plausible, and found 
that many methylation traits cause changes in gene expression.
